Model

### 2020-02-15 stats/model.Rmd
visualize model comp

x <- sample(1:length(unique(model_pred_prag$iteration)), 200)

@@

@@

@@

>>>>

x <- sample(1:length(unique(model_pred_prag$iteration)), 120)

@@

x_fb <- sample(1:length(unique(model_pred_prag_fb$iteration)), 100)

@@

```{r}
ggsave("../graphs/pred_.pdf", width = 10, height = 3, scale = 1)
```

@@

# Comparing models

## Parameters

com_item_params <- bind_rows(
  item_params%>%mutate(model="pragmatic"),
  item_params_fb%>%mutate(model="fullBayes")
)

ggplot(com_item_params, aes(x = value, fill = model, group = paste(model,chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter ~ item, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")

com_global_params <- bind_rows(
  global_params%>%mutate(model="pragmatic"),
  global_params_fb%>%mutate(model="fullBayes")
)

ggplot(com_global_params, aes(x = value, fill = model, group = paste(model,chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")

```{r}
ggsave("../graphs/item_params_by_model.pdf", width = 8, height = 3, scale = 1.5)
```

## Model predictions

```{r}
plot_model_comp <- bind_rows(
plot_model_prag_line,
plot_model_prag_line_fb
)

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(data = plot_model_comp, aes(x=age+2,y = pred, col = model, group = interaction(chain,iteration)),size = .2, alpha = .1)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3, span = 1, size = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol()+
  theme(legend.position = "bottom")
```

```{r}
ggsave("../graphs/predictions_by_model.pdf", width = 8, height = 3, scale = 1.5)
```
